# Web-enabled and Cross-platform SAM via Shiny

First make sure you have a very recent version of R or RStudio.

Next install required packages. Cut and paste what's below in an R session. You only need to do this once.

```{r, eval = FALSE}
install.packages(c("matrixStats", "GSA", "shiny", "openxlsx"))
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("impute")

#install.packages("devtools") if devtools not installed
#library(devtools)
#install_github("cran/samr")
install.packages("samr")
```

You may need to download R tools: 

https://cran.r-project.org/bin/windows/Rtools/

Then, you may run SAM any time in an R session as follows.

```{r}
library(shiny)
library(impute)
runGitHub("SAM", "MikeJSeo")
```

That will bring up a browser window with a user interface. More details are provided in the sam-manual.pdf in this directory.
Data examples and sample output are in a seperate folder to view. 

GSA.correlate.revised.R, GSA.listsets.revised.R, and GSA.plot.revised.R are revised version of the function in GSA. server.r and ui.r contains the main code that generates the GUI. 

Please post to the group regarding any issues. This will help us ensure we have all the kinks ironed out before merging the code 
into the next version of the `samr` package.

Note that users should use Firefox or Chrome as the _default_browser on Windows: IE will not work. 

Thank you,    
Michael Seo